A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-12 manuscript.Rmd
restructure headings

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: references.bib
---

@@

### Preregestration (optional)

@@

### Internal Dependencies

@@

### External Dependencies

@@

#### renv (alternative)

#### Singularity (optional)

## Analyzing Data

<!-- Hands on: add data via automate() -->
<!-- Hands on: automatically download data via manually editing the Makefile -->

### Data Integrity (optional)

@@

### Anonymising Data (optional)

@@

## Peer Review (optional)

## Post Publication Review (optional)

## Archiving

@@

## Checklist

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

@@

## Preregestration (optional)

@@

# Analyzing Data

## Internal Dependencies

@@

## External Dependencies

@@

### renv (alternative)

### Singularity (optional)
<!-- Hands on: add data via automate() -->
<!-- Hands on: automatically download data via manually editing the Makefile -->

## Data Integrity (optional)

@@

## Anonymising Data (optional)

@@

# Peer Review (optional)

# Post Publication Review (optional)

# Archiving

@@

# Checklist
